### 2023-10-25 generalExploration.Rmd
patch correcting deaths and #1

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing
            population[[ind]]$age=population[[ind]]$age+1

@@

            ##marriage
            if(population[[ind]]$age>18 & population[[ind]]$partner <0){
                print("marriage attempt")
                if(runif(1)<m){
                    potential=sapply(population,function(i,s)if(i$age>18 & i$partner<0 & i$sex != s )return(i$id),s=population[[ind]]$sex)
                    potential=unlist(potential)
                    print(potential)
                    if(length(potential)>0){
                        if(length(potential)==1)partner=potential
                        else partner=sample(potential,1)
                        population[[ind]]$partner=partner
                        population[[partner]]$partner=ind
                        newcom=ifelse(runif(1)<rho,population[[ind]]$community,population[[partner]]$community)
                        population[[ind]]$community=population[[partner]]$community=newcom
                        print(paste("marriage",ind,partner,"moving all to",newcom,":",population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }
            if(runif(1)<d){
                if(partner>0) population[[partner]]$partner=-1
                population[i]=NULL
                print(paste("dead ind",i))
            }
        }

@@

        ##pm transmission
        #quickly summarize
        popsum[[time]]=sapply(names(population[lengths(population)>1][1]),function(n)table(sapply(population,"[[",n)))
        size=table(sapply(population,"[[","community"))
        initcomus$size=size
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }
}

>>>>

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind[[i]])){
            ##ageing
            population[[ind]]$age=population[[ind]]$age+1

@@

            ##marriage
            if(population[[ind]]$age>18 & population[[ind]]$partner <0){
                print("marriage attempt")
                if(runif(1)<m){
                    potential=sapply(population,function(i,s)if(i$age>18 & i$partner<0 & i$sex != s )return(i$id),s=population[[ind]]$sex)
                    potential=unlist(potential)
                    print(potential)
                    if(length(potential)>0){
                        if(length(potential)==1)partner=potential
                        else partner=sample(potential,1)
                        population[[ind]]$partner=partner
                        population[[partner]]$partner=ind
                        newcom=ifelse(runif(1)<rho,population[[ind]]$community,population[[partner]]$community)
                        population[[ind]]$community=population[[partner]]$community=newcom
                        print(paste("marriage",ind,partner,"moving all to",newcom,":",population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }

            #Handle deaths
            if(runif(1)<d){
                if(partner>0) population[[partner]]$partner=-1
                population[i]=NULL
                print(paste("dead ind",i))
            }
        }

@@

        #quickly summarize
        popsum[[time]]=sapply(names(population[lengths(population)>1][1]),function(n)table(sapply(population,"[[",n)))
        size=table(sapply(population,"[[","community"))
        initcomus$size=size
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }
}
